Late Pleistocene stone artefact technology at Mau A, Yen Bai, Northern Vietnam

### 2022-03-17 analysis/paper/paper.Rmd
Added in new schematic figure for flake landmarks
temporary subsitution of svg file for png due to issues with labels not printing correctly with the svg file

```{r, schematic-figure, fig.cap="Schematic figure showing both the intial measurements that were used to generate our landmarks and the location of our landmarks on a hypothetical flake. A, B, C, D, and E are the top horizontal measurement, width at a quarter of the maximum length, maximum dimension length, width at a quarter of the maximum length, and width at three quarter of the maximum length respectively. Points 1 through 9 are all of the landmarks generated from measurements A through E."}
# knitr::include_graphics(here::here("analysis/flake-measurements-schematic-figure.png"))
```

@@

plot_grid(PC1_contrib +
             theme(axis.text = element_text(size = 5)),
          PC2_contrib + 
             theme(axis.text = element_text(size = 5)),
          labels = "AUTO"
  )

>>>>

```{r, schematic-figure, fig.cap="Schematic figure showing both the intial measurements that were used to generate our landmarks and the location of our landmarks on a hypothetical flake. A, B, C, D, and E are the top horizontal measurement, width at a quarter of the maximum length, maximum dimension length, width at a quarter of the maximum length, and width at three quarter of the maximum length respectively. Points 1 through 9 are all of the landmarks generated from measurements A through E."}
knitr::include_graphics(here::here("analysis/figures/flake-measurements-schematic-figure-temp.png"))
```

@@

temp <- plot_grid(PC1_contrib +
             theme(axis.text = element_text(size = 5)),
          PC2_contrib + 
             theme(axis.text = element_text(size = 5)),
          labels = "AUTO"
  )
